Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/discussion.tex
revise result for RQ2

%\subsection{Binary Classification}
\subsection{How much impact of unclear class on model construction?}
\pick{This topic of discuss should be changed....}
 % noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear or undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our training set.
This leaves us with 209 remaining samples, all without a disagreement.
By performing cross-validation using these samples, we obtained a much better F$_1$ score of 0.896.

However, we could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
But interestingly, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{posneg}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}

@@

\subsection{Can the determined thresholds in this study be used to other projects?} 
This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets. This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.

>>>>

%\subsection{Binary Classification}
%\subsection{How much impact of unclear class on model construction?}
%\pick{This topic of discuss should be changed....}
% % noisy data, and binary classification
%
% 
% 
%Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
%This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
%
%Another approach we tried is to perform a \emph{binary classification}.
%This means we assume that there are no unclear or undetermined comments; only useful and useless.
%For this, we removed the samples with 1 and 2 \texttt{YES} votes from our training set.
%This leaves us with 209 remaining samples, all without a disagreement.
%By performing cross-validation using these samples, we obtained a much better F$_1$ score of 0.896.
%
%However, we could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
%But interestingly, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification. 
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=2.5in]{posneg}
%\caption{The amount of comments by score classified by the binary classifier.}
%\label{fig:binary}
%\end{figure}

@@

\subsection{Can the determined thresholds in this study be used to other projects?} 
\pick{need to be revised}
This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets. This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.

### 2014-07-30 sections/results.tex
revise result for RQ2

\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{cccccc}
\hline
Result from & \multicolumn{4}{c}{Results from manual assessment}  & \multirow{3}{*}{Precision}\\ \cline{2-5}
Classification &  Useless  & Unclear  & Unclear & Useful \\
Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 95 & 0.709\\
Useless & 69 & 23 & 7 & 6 &  0.657\\
Overlap & 1 & 1 & 0 & 1 & - \\
Undetermined & 12 & 24 & 20 & 20 & - \\
\hline
Recall & 0.812 & - & - & 0.778\\ \hline 
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random model as twice.}

@@

To answer this question, timestamps are recorded as three people voted on each comment.
Since three people work in their leisure time, there is much variability in the time between each vote.
Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.

On average, it takes 28 seconds to assess each comment.
However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
This also suggests that the time to assess each comment is not normally distributed.
The standard deviation is 45 seconds.

To estimate the total time for us to assess these 318 comments,
we multiplied the average time by the number of comments and the number of people.
This results in 7.42 person hours.

However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
That means that about 77\% of the effort is saved.

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset,
which may suggest that our model will have a similar performance in the real data.

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Classification & over all samples & only training data \\ \hline
useful & 42.8\% & 41.8\% \\
useless & 33.7\% & 33.1\% \\
undetermined & 23.5\% & 25.1\% \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}

>>>>

\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{cccccc}
\hline
Result from & \multicolumn{4}{c}{Results from manual assessment}  & \multirow{3}{*}{Precision}\\ \cline{2-5}
Classification &  Useless  & Unclear  & Unclear & Useful \\
Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful Class & 3 & 12 & 24 & 95 & 0.709\\
Useless Class & 69 & 23 & 7 & 6 &  0.657\\
Overlap & 1 & 1 & 0 & 1 & - \\
Undetermined & 12 & 24 & 20 & 20 & - \\
\hline
Recall & 0.812 & - & - & 0.778\\ \hline 
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random  classification models as twice.}

@@

Automatic system generally known that it can  save human effort  and also reduce erroneous from human. We analyse the results to determine the performance of our models. Moreover, we also consider scalability of our models as it only validated in the small set of comments. \pick{Trying to explain why we considering this}

\textbf{Cost Efficiency:} We determined cost efficiency in terms of time use for manual assessment. For 318 comments in RQ1, we found that the manual assessment took \TODO{XX} person hours on average. However, this time can be inaccurate since practitioners did not assess under the controlled environment. To be more precise, we considered only the interval time less ten minutes. The average interval time is 28 seconds. Thus, for 318 comments, the assessment time should be 7.42 person hours. Using the same average interval time for all 10,583 comments, we can imply that the manual assessment time would be 82.3 person hours. When applying our approach to classify these all comments, the models left only 23.5\% of comments for manual assessment (undetermined comments) as shown in Table  \ref{tb:percent}. This means that an additional manual assessment needs only 19.34 person hours for these undermined comments which save human effort 76.5\%.

%To answer this question, timestamps are recorded as three people voted on each comment.
%Since three people work in their leisure time, there is much variability in the time between each vote.
%Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
%
%On average, it takes 28 seconds to assess each comment.
%However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
%This also suggests that the time to assess each comment is not normally distributed.
%The standard deviation is 45 seconds.
%
%To estimate the total time for us to assess these 318 comments,
%we multiplied the average time by the number of comments and the number of people.
%This results in 7.42 person hours.
%
%However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
%By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
%That means that about 77\% of the effort is saved.

\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores. The classification of useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. We conjecture that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with \texttt{YES} = 1 can be useless comments. This might be an error prone from the manual assessment. To verify this, we asked practitioners to re-examined the unclear comments. We found that there are \TODO{XX}\% of 66 unclear comments changed an answer. This indicates that ......

%As the manual classification can be subjective, these comments were not received three voting scores.

\textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset,
which may suggest that our model will have a similar performance in the real data.

\begin{table}[!t]
\caption{Percentage of classifications results for all comments in the \texttt{qtbase} project }
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{c|c|c}
\hline

Result from & Sample Comments   &  All Comments \\ \cline{2-3}
Classification Models &  318 comments  & 10,583 comments \\ \hline \hline
Useful Class  & 41.8\% & 42.8\% \\
Useless Class   & 33.1\%  & 33.7\% \\
undetermined  & 25.1\% & 23.5\% \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}
